Crossing Origins by Crossing Formats

### 2012-11-22 main.tex
Section Crossing-origins neearly complete.

In this section we generalize the problem and describe how it can be abused to
circumvent the same-origin policy.

\subsection{Polyglots}

@@

A polyglot is composed from various constructs that are either common between
languages; or constructs that are language specific, but carrying different
meaning in each language. To maintain validity across languages, one must ensure
that language specific constructs are not interpreted by other languages. This
is often accomplished by hiding the parts of the code specific to one language,
in parts interpreted as comments or text of another.

@@

\subsection{Malicious polyglots}

A polyglot can be used for malicious purposes if there is a difference between
the expected execution environment and the actual environment it is executed in.
If the content is verified to be benign in

@@

It is possible to create such a polyglot by mixing content, that is benign when
verified, with content, that is malicious when executed. The verification
process will see the benign content and allow it, but subsequently the malicious
content is executed.

@@

@@

The target in this scenario is a user of the vulnerable website. The polyglot is
served in the benign format on the vulnerable server. However, the attack is
initiated from a page belonging to the attacker. While the user is logged in to
the service that the vulnerable website provides, the user unsuspectingly visits
the attackers malicious website. The page embeds the polyglot content, but
coerces it to be interpreted as the malicious format. The attacker can now
exploit the vulnerability, either by making requests to the vulnerable website
in the context of the user; or by extracting information about the user that is
stored on the vulnerable website.

@@

The PDF format is a widely used, text based format with powerful capabilities.
It can be used for displaying text, rendering graphics, animation and dynamic
content. It is also a container format which allows for embedding of other files
and formats. This and the fact that it is designed to be robust against errors,
provides us with a format that is powerful, flexible and ideal for creating
malicious polyglots.

%Several design choices

@@

\subsubsection{Cross-origin communication}

@@

\subsubsection{The object-tag}

@@

The object-tag is used to embed content, which requires a plug-in
to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the object tag allows a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of which MIME-type the server returns
and it is up to the plug-in to respond to and handle the content it is served.

As it turns out, various plug-ins deal with the situation differently. The Chrome browser
built-in PDF reader refuses to render content that was served with an inappropriate 
MIME-type. The Java plug-in used to ignore the MIME-type, but after several 
vulnerabilities were disclosed, this behavior was changed.

@@

\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
\%PDF-\
trailer<</Root<</Pages<<>>>>>>
\end{lstlisting}

>>>>

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the \emph{Same-Origin Policy}. We begin by 
generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

\subsection{Crossing formats}

@@

A polyglot is composed from various constructs that are either common between
languages; or constructs that are language specific, but carrying different
meaning in each language. To maintain validity across languages, one must ensure
that language specific constructs are not interpreted by other languages. This
is often accomplished by hiding the parts of the code specific to one language,
in parts interpreted as comments or plain text of another.

@@

\paragraph{Malicious polyglots}

% What is a malicious polyglot? - One part benign one part malicious

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content would be interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

Even if a verification process exists, it would verify that the content is valid 
in the expected context. Due to the nature of the polyglot, the content would be 
verified as valid and benign, but subsequently the malicious
content is executed.

In a web context, 
% Characteristics of a malicious polyglot

% Malicious polyglots in literature; gifar, chameleon, cross-origin css attacks

% We have identified two classes of malicious polyglots; those based on syntax injection, and those based on content repurposing.

If the content is verified to be benign in

@@

It is possible to create such a polyglot by mixing content, that is benign when
verified, with content, that is malicious when executed. The verification
process will see the benign content and allow it

@@

\subsection{Crossing origins}

By crossing origins we mean being able to request and access content
which is normally restricted under the Same-Origin Policy (SOP). 
The SOP dictates that a two document can only access each others 
content and resources if they share the same origin. Similarly this applies to communication as 
well; a document can only directly communicate with the server from which it originated. 
This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
intentional relaxing of the SOP.

While there are exceptions to this policy, e.g. images, scripts, and style sheets 
are allowed to be included as resources across origins, access to these resources is 
carefully restricted to prevent information leaks. As an example, the including 
document is prevented from accessing the image data of images loaded across 
origins.

Not all elements are as carefully restricted from information leaks as images. 
Scripts loaded across origins become part of the document and inherit the 
origin of the including document, which allows the script to communicate with the 
server from which the \emph{document} originated. Such scripts are also able to interact 
with the document, e.g. by adding nodes, which in turn require new content to be 
requested. Since these requests are not restricted by the SOP, this creates a side 
channel that permits cross-origin information leakage. At the same time, the including document
is prevented from inspecting the source of the script and can only observe the public 
side-effects that the script produce as it is executed.

Other examples of problematic elements include the object- and embed-tags. These 
tags allow inclusion of resources that might require a 
plug-in to run. As with images, the content handled by the plug-in retains its origin, 
but the browsers are forced to rely on the plug-ins to employ correct security 
measures to prevent information leaks. While the containing page is restricted 
from directly accessing the content handled by the plug-in, a number of plugins provide 
an API for interacting with the plug-in and the data. As we will show, this can easily lead to 
to cross-origin information leaks.

@@

The target in this scenario is a user of the vulnerable website. The polyglot is
served in the benign format on the vulnerable server. While the user is logged in to
the service that the vulnerable website provides, the user unsuspectingly visits
the attackers malicious website. The page embeds the polyglot content, but
coerces the browser to interpret the content as the malicious format. 
How  on the capabilities of the malicious format, 
The attacker can now
exploit the vulnerability, either by making requests to the vulnerable website
in the context of the user; or by extracting information about the user that is
stored on the vulnerable website.

@@

The PDF format is a widely used, text based format with powerful capabilities.
It is capable of displaying text, rendering graphics, animation and dynamic
content. It is a container format which allows for embedding of other files
and formats. This and the fact that it is designed to be robust against errors,
provides us with a format that is powerful, flexible and ideal for creating
malicious polyglots.

% Several design choices

% - Error tolerant parsing
% - Execute JavaScript
% - Embed flash files
% - Launch commands

@@

\subsubsection{PDF communication channels}

@@

\subsection{The object-tag}

@@

The object-tag is used to embed content, which requires a browser plug-in
to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the object tag allows a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of which MIME-type the server returns
and it is up to the plug-in to respond to and handle the content it is served.

As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
built-in PDF reader refuses to render content that was served with an inappropriate 
MIME-type. The Java plug-in used to ignore the MIME-type, but after several 
vulnerabilities were disclosed, this behavior was changed.

@@

\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
%PDF-
trailer<</Root<</Pages<<>>>>>>
\end{lstlisting}
